Diversification of Australian blind snakes

### 2022-12-01 manuscript.Rmd
update big summary of discussion

Our study

BIG SUMMARY

@@

IMPORTANCE OF THIS TECHNICAL ASPECT OF THIS WORK 
- We show that reconstruction of localised paleo environment is possible and argue that it is more appropriate as a correlate to diversification rates. 
- Building these paleoclimate models for regional areas will be of interested for studies where species are geographically restricted. 
- Studies that aim to understand how aridification affect diversification rates in Australia should apply paleoclimate or use them to inform models and inferences. 
- For example, models like NEMo allows bounding ancestral niche with estimates of paleo climate.

>>>>

With 47 recognised species, the mostly Australian-endemic genus *Anilios* is currently the most diverse genus of scolecophidia in the world. In this study we inferred the the genus has a tropical grassland origin. Within a few million years the ancestral lineage diversified rapidly and the tropical grassland biome served as a major source of diversification as lineages transitioned into what we now consider the arid biome and subsequently into the mediterranean and temperate XXXXgrassland biomes. 
We found that paleo aridity index provides the best fit to diversification dynamics observed in our blind snake tree. 
Although aridification has been shown to accelerate diversification in other groups of vertebrates, we found that *Anilios* blind snakes follow a different trajectory. Increased aridity from the late Miocene-early Pleistocene coincided with reduced diversification rates for genus.

@@

IMPORTANCE OF THIS TECHNICAL ASPECT OF THIS WORK 
- We show that reconstruction of localised paleo environment is possible and argue that it is more appropriate as a correlate to diversification rates. 
- Building these paleoclimate models for regional areas will be of interested for studies where species are geographically restricted. 
- Studies that aim to understand how aridification affect diversification rates in Australia should apply paleoclimate or use them to inform models and inferences. 
- For example, models like NEMo allows ancestral niche to be informed by paleo environment as a prior.
